Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-07-30 main.tex
Removing doubled citations and comments

%mm should most of this material be in the introduction, and just the last two sentences be here?
Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars. In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}). Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances. In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models. However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies. To build towards this, we characterize the metal evolution and distributions in our galaxy below.

% Classic chemical evolution models often adopt the simplifying assumption that metals from newly formed stars are instantly deposited back into the ISM \textbf{(examples)}. With added complication, this instantaneous recycling approximation (IRA) can be expanded upon by taking into account individual stellar lifetimes (references) which have been shown to produce significant variations in stellar abundances (references) as compared to IRA models. However, even in this new model it is unlikely that whatever fraction of a star's yields that remains in the ISM instantaneously enriches star forming gas. Rather, these yields are first injected through a hot phase (stellar winds, H~{\sc ii} regions, supernovae), cooling over time into star forming gas. (refs for models accounting for this). We investigate this process in our simulations below, first by outlining a new analytic description of metal distributions in the ISM.

>>>>

%mm should most of this material be in the introduction, and just the last two sentences be here?
%   AE: I agree this is mostly redundant. I removed this
%Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars. In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}). Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances. 
In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models. However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies. To build towards this, we characterize the metal evolution and distributions in our galaxy below.
